Starcode: sequence clustering based on all-pairs search

### 2015-01-18 doc/document.tex
Added software versions.

\begin{table}[h]
\centering
\caption{Software execution options used in simulation benchmark.}
%\resizebox{\columnwidth}{!}{
\begin{tabular}{l|l}
    \bf{software} & \bf{command-line options}\\
    \hline
    starcode & \texttt{starcode -d3}\\
    slidesort & \texttt{slidesort\_v2 -d 3 -t E -c DNA}\\
    cd-hit-est & \texttt{cd-hit-est -n 9 -c 0.9 -M 0 -r 0}\\
    seed & \texttt{SEED --mismatch 3}\\
\end{tabular}
%}
\label{tab:params1}
\end{table}

\begin{table}[h]
\centering
\caption{Software execution options used in real data benchmark.}
%\resizebox{\columnwidth}{!}{
\begin{tabular}{l|l}
    \bf{software} & \bf{command-line options}\\
    \hline
    starcode & \texttt{starcode -d3}\\ 
    slidesort & \texttt{slidesort\_v2 -d 3 -u -t E -c DNA}\\
    cd-hit-est & \texttt{cd-hit-est -n 8 -c 0.94 -M 0}\\
    seed & \texttt{SEED --mismatch 3 --shift 3}\\ 
    rainbow & \texttt{rainbow cluster -m 3}
\end{tabular}
%}
\label{tab:params2}
\end{table}

>>>>

\begin{table}[h]
\centering
\caption{Software execution options used in simulation benchmark.}
%\resizebox{\columnwidth}{!}{
\begin{tabular}{l|l}
    \bf{software} & \bf{command-line options}\\
    \hline
    starcode-1.0 & \texttt{starcode -d3}\\
    slidesort-2 & \texttt{slidesort\_v2 -d 3 -t E -c DNA}\\
    cd-hit-est-4.6.1 & \texttt{cd-hit-est -n 9 -c 0.9 -M 0 -r 0}\\
    seed-1.4.1 & \texttt{SEED --mismatch 3}\\
\end{tabular}
%}
\label{tab:params1}
\end{table}

\begin{table}[h]
\centering
\caption{Software execution options used in real data benchmark.}
%\resizebox{\columnwidth}{!}{
\begin{tabular}{l|l}
    \bf{software} & \bf{command-line options}\\
    \hline
    starcode-1.0 & \texttt{starcode -d3}\\ 
    slidesort-2 & \texttt{slidesort\_v2 -d 3 -u -t E -c DNA}\\
    cd-hit-est-4.6.1 & \texttt{cd-hit-est -n 8 -c 0.94 -M 0}\\
    seed-1.4.1 & \texttt{SEED --mismatch 3 --shift 3}\\ 
    rainbow-2.0.3 & \texttt{rainbow cluster -m 3}
\end{tabular}
%}
\label{tab:params2}
\end{table}
